Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-03-01 main_paper.tex
Fix small typos in proof of Theorem 2
Tweak presentation of author affiliations

\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{All authors:
Department of Economics, Iowa State University. 260 Heady Hall, Ames, IA  50011.
Bartalotti: Email: bartalot@iastate.edu. Calhoun: gcalhoun@iastate.edu.
He: yanghe@iastate.edu.}}

>>>>

\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{%
  All authors: Department of Economics, Iowa State University.
  260 Heady Hall, Ames, IA 50011.
  Bartalotti: \protect\url{bartalot@iastate.edu};
  Calhoun: \protect\url{gcalhoun@iastate.edu} and
  \protect\url{http://gray.clhn.org};
  He: \protect\url{yanghe@iastate.edu}.}}
